Supplemental Information:\\ Harnessing Design Principles from Glass Sponges for Structurally Robust Lattice Structures

### 2018-09-12 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.

\section{Additional numerical results}
\KB{add here all additional numerical results}
In this section we validate the RVE domain size by checking the response of larger domain sizes on the critical buckling value. This ensures that there does not exist another critical buckling mode that is limited by our choice of RVE.

@@

>>>>

@@

\section{Additional numerical results}
In this section we validate the RVE domain size by checking the response of larger domain sizes on the critical buckling value. This ensures that there does not exist another critical buckling mode that is limited by our choice of RVE.
